Modeling and analyzing the Corona-virus warning app with the Isabelle Infrastructure framework

### 2020-07-11 paper.tex
techn. part: fixed TODOs (i.e. citations of DP-3T whitepaper)

\newcommand{\symb}[1]{\makebox{\it #1}} 
\newcommand\ie{i.e.\!\,, }
\newcommand\rel{Re${\cal{L}}$}
\newcommand{\TODO}[1]{\textcolor{red}{\textbf{[TODO:#1]}}}
\newcommand*{\TODOfn}[2][noteC]{\TODO[#1]{[\footnote{\TODO[#1]{#2}}]}}
\newcommand*{\TODOref}[2][todoC]{\TODOfn[#1]{\textbf{BIB-REF}: #2}}
\newcommand\ttand{\mbox{{$\land$}}}
\newcommand\ttor{\mbox{{$\lor$}}}
\newcommand\ttcap{\mbox{{$\cap$}}}
\newcommand\ttcup{\mbox{{$\cup$}}}
\newcommand\ttfun{\mbox{{$\Rightarrow$}}}
\newcommand\ttmimp{\mbox{{$\Longrightarrow$}}}
\newcommand\ttimp{\mbox{{$\longrightarrow$}}}
\newcommand\ttequiv{\mbox{{$\equiv$}}}
\newcommand\ttexists{\mbox{{$\exists$}}}
\newcommand\ttforall{\mbox{{$\forall$}}}
\newcommand\ttneg{\mbox{{$\neg$}}}
\newcommand\ttneq{\mbox{{$\neq$}}}
\newcommand\ttin{\mbox{{$\in$}}}
\newcommand\ttnin{\mbox{{$\notin$}}}
\newcommand\ttImp{\mbox{{$\Longrightarrow$}}}
\newcommand\ttlam{\mbox{\( \lambda \)}}
\newcommand\tttimes{\mbox{\( \times \)}}
\newcommand\ttlbrack{\mbox{\(\llbracket\)}}
\newcommand\ttrbrack{\mbox{\( \rrbracket \)}}
\newcommand\noie{\textit{i.e.},\xspace}
\newcommand\eg{~\textit{e.g.},\xspace}
\newcommand\noeg{\textit{e.g.},\xspace}
\newcommand\ttatI{\mbox{\( @_G \)}}
\newcommand\ttto[1]{\mbox{{$\to^{#1}$}}}
\newcommand\ttleq{\mbox{{$\le$}}}
\newcommand\ttrelI{\mbox{{$\to_{i}$}}}
\newcommand\ttrelIstar{\mbox{{$\to^*$}}}
\newcommand\ttrel[1]{\mbox{{$\to_{#1}$}}}
\newcommand\ttrelstar[1]{\mbox{{$\to_{#1}^*$}}}
\newcommand\ttalpha{\mbox{{$\alpha$}}}
\newcommand\ttsupseteq{\mbox{{$\supseteq$}}}
\newcommand\ttupdownarrow{\mbox{{$\Updownarrow$}}}
\newcommand\ttbigcap{\mbox{{$\bigcap$}}}
\newcommand\tttau{\mbox{{$\tau$}}}
\newcommand\ttsubseteq{\mbox{{$\subseteq$}}}
\newcommand\ttf{\mbox{{$f$}}}
\newcommand\ttvdash{\mbox{{$\vdash$}}}
\newcommand\ttref[1]{\mbox{\(\sqsubseteq_{#1}\)}}
\newcommand\ttrefV{\mbox{{$\sqsubseteq_V$}}}
\newcommand{\ttcalN}[1]{\mbox{{${\mathcal{N}}_{\texttt{#1}}$}}} 
\newcommand\ttNatt{\mbox{{$\mathcal{N}$}}}
\newcommand\ttattand[1]{\mbox{{$\oplus_{\wedge}^{#1}$}}}
\newcommand\ttattor[1]{\mbox{{$\oplus_{\vee}^{#1}$}}}
\newcommand\ttsigma{\mbox{{$\sigma$}}}
\newcommand\ttmref[1]{\mbox{{$\sqsubseteq_{#1}$}}}
\newcommand\ttmeref{\ttmref{\mathcal{E}}}
\newcommand\ttsn{\mbox{{\texttt{s}$_0$}}}
\newcommand\ttsigmap{\mbox{{$\sigma'$}}}
\newcommand\ttecal{\mbox{$\mathcal{E}$}}
%\newcommand\ttimg{\mbox{$\triangleleft$}}
\newcommand\ttimg{\mbox{\texttt{`}}}

@@

For the DP-3T Ephemeral Ids \TODOref{DP-3T Whitepaper}, for each day $t$ a seed $SK_t$
is used to generate a list of length $n = 24 * 60 / L$, where $L$ is the duration for which
the Ephemeral Ids are posted by the smart phone
\begin{ttbox}
  EphId1 || ... || EphIdn = PRG(PRF(SKt,``broadcast key''))
\end{ttbox} 
``where PRF is a pseudo-random function (e.g., HMAC-SHA256), ``broadcast key'' is a
fixed, public string, and PRG is a pseudorandom generator (e.g. AES in counter mode)'' \TODOref{DP-3T Whitepaper}.

>>>>

\newcommand{\symb}[1]{\makebox{\it #1}} 
\newcommand\ie{i.e.\!\,, }
\newcommand\rel{Re${\cal{L}}$}
%\newcommand{\TODO}[1]{\textcolor{red}{\textbf{[TODO:#1]}}}
%\newcommand*{\TODOfn}[2][noteC]{\TODO[#1]{[\footnote{\TODO[#1]{#2}}]}}
%\newcommand*{\TODOref}[2][todoC]{\TODOfn[#1]{\textbf{BIB-REF}: #2}}
\newcommand\ttand{\mbox{{$\land$}}}
\newcommand\ttor{\mbox{{$\lor$}}}
\newcommand\ttcap{\mbox{{$\cap$}}}
\newcommand\ttcup{\mbox{{$\cup$}}}
\newcommand\ttfun{\mbox{{$\Rightarrow$}}}
\newcommand\ttmimp{\mbox{{$\Longrightarrow$}}}
\newcommand\ttimp{\mbox{{$\longrightarrow$}}}
\newcommand\ttequiv{\mbox{{$\equiv$}}}
\newcommand\ttexists{\mbox{{$\exists$}}}
\newcommand\ttforall{\mbox{{$\forall$}}}
\newcommand\ttneg{\mbox{{$\neg$}}}
\newcommand\ttneq{\mbox{{$\neq$}}}
\newcommand\ttin{\mbox{{$\in$}}}
\newcommand\ttnin{\mbox{{$\notin$}}}
\newcommand\ttImp{\mbox{{$\Longrightarrow$}}}
\newcommand\ttlam{\mbox{\( \lambda \)}}
\newcommand\tttimes{\mbox{\( \times \)}}
\newcommand\ttlbrack{\mbox{\(\llbracket\)}}
\newcommand\ttrbrack{\mbox{\( \rrbracket \)}}
\newcommand\noie{\textit{i.e.},\xspace}
\newcommand\eg{~\textit{e.g.},\xspace}
\newcommand\noeg{\textit{e.g.},\xspace}
\newcommand\ttatI{\mbox{\( @_G \)}}
\newcommand\ttto[1]{\mbox{{$\to^{#1}$}}}
\newcommand\ttleq{\mbox{{$\le$}}}
\newcommand\ttrelI{\mbox{{$\to_{i}$}}}
\newcommand\ttrelIstar{\mbox{{$\to^*$}}}
\newcommand\ttrel[1]{\mbox{{$\to_{#1}$}}}
\newcommand\ttrelstar[1]{\mbox{{$\to_{#1}^*$}}}
\newcommand\ttalpha{\mbox{{$\alpha$}}}
\newcommand\ttsupseteq{\mbox{{$\supseteq$}}}
\newcommand\ttupdownarrow{\mbox{{$\Updownarrow$}}}
\newcommand\ttbigcap{\mbox{{$\bigcap$}}}
\newcommand\tttau{\mbox{{$\tau$}}}
\newcommand\ttsubseteq{\mbox{{$\subseteq$}}}
\newcommand\ttf{\mbox{{$f$}}}
\newcommand\ttvdash{\mbox{{$\vdash$}}}
\newcommand\ttref[1]{\mbox{\(\sqsubseteq_{#1}\)}}
\newcommand\ttrefV{\mbox{{$\sqsubseteq_V$}}}
\newcommand{\ttcalN}[1]{\mbox{{${\mathcal{N}}_{\texttt{#1}}$}}} 
\newcommand\ttNatt{\mbox{{$\mathcal{N}$}}}
\newcommand\ttattand[1]{\mbox{{$\oplus_{\wedge}^{#1}$}}}
\newcommand\ttattor[1]{\mbox{{$\oplus_{\vee}^{#1}$}}}
\newcommand\ttsigma{\mbox{{$\sigma$}}}
\newcommand\ttmref[1]{\mbox{{$\sqsubseteq_{#1}$}}}
\newcommand\ttmeref{\ttmref{\mathcal{E}}}
\newcommand\ttsn{\mbox{{\texttt{s}$_0$}}}
\newcommand\ttsigmap{\mbox{{$\sigma'$}}}
\newcommand\ttecal{\mbox{$\mathcal{E}$}}
%\newcommand\ttimg{\mbox{$\triangleleft$}}
\newcommand\ttimg{\mbox{\texttt{`}}}

@@

For the DP-3T Ephemeral Ids \cite{dp3t:wp}, for each day $t$ a seed $SK_t$
is used to generate a list of length $n = 24 * 60 / L$, where $L$ is the duration for which
the Ephemeral Ids are posted by the smart phone
\begin{ttbox}
  EphId1 || ... || EphIdn = PRG(PRF(SKt,``broadcast key''))
\end{ttbox} 
``where PRF is a pseudo-random function (e.g., HMAC-SHA256), ``broadcast key'' is a
fixed, public string, and PRG is a pseudorandom generator (e.g. AES in counter mode)'' \cite{dp3t:wp}.
